\texttt{gwsnr}: A Python Package for Efficient SNR Calculation of GWs

### 2025-06-21 arxiv/paper_old.tex
mac

        \author[1]{Phurailatpam Hemantakumar}
          \author[1]{Otto Akseli HANNUKSELA}

@@

The \emph{\texttt{gwsnr}} package now incorporates an artificial neural
network (ANN) model, developed using \emph{\texttt{TensorFlow}} (Abadi
et al. (2015)) and \emph{\texttt{sklearn}} (Pedregosa et al. (2011)), to
rapidly estimate the Pdet in binary black hole (BBH) systems using the
IMRPhenomXPHM waveform approximant. This complex IMR waveform model
accounts for spin-precessing systems with subdominant harmonics. The ANN
model is especially useful when precise signal-to-noise ratio (SNR)
calculations are not critical, providing a quick and effective means of
estimating Pdet. This value indicates detectability under Gaussian noise
by determining if the SNR exceeds a certain threshold. Trained on a
large dataset from the \emph{\texttt{ler}} package, the ANN model uses
`partial scaled SNR' values as a primary input, reducing input
dimensionality from 15 to 5 and enhancing accuracy. This approach offers
a practical solution for assessing detectability under specified
conditions. Other similar efforts with ANN models are detailed in
Chapman-Bird et al. (2023), Gerosa et al. (2020) etc.

@@

>>>>

        \author[1]{Hemantakumar Phurailatpam}
          \author[1]{Otto Akseli HANNUKSELA}

@@

The \emph{\texttt{gwsnr}} package now incorporates an artificial neural
network (ANN) model, developed using \emph{\texttt{TensorFlow}} (Abadi
et al. (2015)) and \emph{\texttt{sklearn}} (Pedregosa et al. (2011)), to
rapidly estimate the Pdet in binary black hole (BBH) systems using the
IMRPhenomXPHM waveform approximant. This complex IMR waveform model
accounts for spin-precessing systems with subdominant harmonics. The ANN
model is especially useful when precise signal-to-noise ratio (SNR)
calculations are not critical, providing a quick and effective means of
estimating Pdet. This value indicates detectability under Gaussian noise
by determining if the SNR exceeds a certain threshold. Trained on a
large dataset from the \emph{\texttt{ler}} package, the ANN model uses
`partial scaled SNR' values as a primary input, reducing input
dimensionality from 15 to 5 and enhancing accuracy. This approach offers
a practical solution for assessing detectability under specified
conditions. Other similar efforts with ANN models are detailed in
Chapman-Bird et al. (2023), Gerosa et al. (2020), Callister et al.
(2024) etc.

In addition to providing trained ANN models for specific configurations,
\emph{\texttt{gwsnr}} offers users the flexibility to develop and train
custom models tailored to their unique requirements. This adaptability
allows for optimization based on variations in detector sensitivity,
gravitational wave properties, and other research-specific factors,
ensuring maximum model effectiveness across different scenarios.

@@

\bibitem[\citeproctext]{ref-Callister2024}
Callister, Thomas A. et al. 2024. {``Neural Network Emulator of the
Advanced LIGO and Advanced Virgo Selection Function.''} \emph{Physical
Review D} 110 (12). \url{https://doi.org/10.1103/physrevd.110.123041}.
